SETI in the Spatial-Temporal Survey Domain

### 2019-04-25 paper/ms.tex
clean comments from removed text out
wednesday progress

%Here I propose one such SETI approach, which utilizes exoplanet-like transit signals coordinated around multiple stars to indicate the presence of an interstellar civilization. In this scenario, artificial occulting objects would act as beacons, being placed in orbit around stars surrounding the central home star system. The orbital period of each artificial satellite would be proportional to the distance from the beacon star to the home star system. If the orbital period versus beacon distance relationship was known, the exact location of the home system could be determined via triangulation (or trilateration) from a subset of the transiting beacons seen by an observer. Current and future exoplanet surveys would be able to detect such spatially coordinated transits around nearby low-mass stars. While contrived, this example highlights the need for SETI researchers to consider the spatial-temporal domain.

@@

%\bf THE POINT: } in this new spatial-temporal domain, we should be looking for things that happen in space, such as over densities of events, or coordination of events like transits.

%{\bf THIS PAPER NEEDS TO BE RETHOUGHT, IN LIGHT OF MORE SPECIFIC PAPER IDEA:}{\it SETI with ZTF}
%
%In the search for extraterrestrial intelligence (SETI), most approaches focus on direct detection of photons originating from transmission or waste energy. These searches occur over a range of wavelength regimes, and assume an extraterrestrial civilization will produce sufficient radiation to be detected apart from their parent star. While this may be feasible at radio wavelengths where Sun-like stars have lower emission, it is much more difficult to outshine the star in the optical regime where many present-day time domain surveys operate. 
%
%
%Blocking a significant fraction of light from a star may instead be much easier than outshining it \cite{arnold2005}. This has led to recent searches for transit-like signatures that may have artificial origins. For example, PAPER demonstrated the observable impact of transits by non-spherical objects \cite{arnold2005a}.
%on the impact of artificial structures on transits. also this work on that:
%\cite{wright2016}.
%recent data from \Kepler \citep{borucki2010}, has found weird transit-like signals
%\cite{boyajian2015}, 
%which some have considered as SETI candidates. However, follow-up observations have yet to yield any confirming signatures, and instead this looks like a YSO w/ comets maybe \citep{lisse2015}.
%
%
%Previous work has suggested looking for SETI signals from interstellar ``beacons''
%\cite{benford2008}
%However, most such work has been focused on using lasers or other means to out-shine a parent star, often observed using spectroscopy \cite{reines2002}. This is a very expensive way to stand out, and a slow way to find it, and so far has no success in discovering ET laser emission \cite{tellis2015}
%\cite{arnold2005} note that objects could be placed at interesting spacing along the orbit to encode a pattern or simple message, demonstrating an intelligent origin. However, very little information can be effectively transmitted using eclipses, even with extreme precision in the recovery.
%\cite{forgan2017} show a galactic-scale communications network of using transits, but note links in the network are only stable for order $10^5$ years as galactic orbital dynamics move things around

%optical seti
%\citep{holder2005} optical pulse SETI 
%
%a review of Schelling points from \citet{wright2017}
%lighthouses \citep{zuluaga2015}
%active and passive SETI in coordination (both temporal and spatial) with galactic events like supernovae 
%\citep{lemarchand1994}
%coordinated times/places, also known as Schelling or Focal points \citep{schelling1960}, are the key to finding people in unknown time/space.
%planets in Earth's transit zone \cite{heller2016} - maybe transits would be aligned for our viewing benefit?
%

% include mantras of "worth doing", "do it almost for free", "reproducible", "portable, do it everywhere", and "outliers are nature papers"

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example: Distribution of Transiting Exoplanets in the {\it Kepler} Field}
%\section{Example 1: Coordinated Transits as ET Beacons}
\label{sec:transit}

@@

\citep{landy1993}

@@

%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=3in]{../figures/delta_per.png}
%\caption{searching for correlation between transit periods and projected separations between all exoplanet systems out to 2deg in the Kepler data. 
%median period differences are computed for bins of separation distance (orange points).
%there is no trend in these medians, indicating a distribution of orbital periods that are random on large scales.}
%\label{fig:2dcor}
%\end{figure}

%%%%%% 
%    > shelve this idea for now, maybe another paper.... 1 demo is enough for this paper, 
%    and it should be actually computed/worked out.
%%%%%% 
%\subsection{Coordinated Transit Networks}
%imagine a Type N civilization with the ability to both travel to nearby star systems, and to build large enough structures in orbit around other stars to produce a visible transit in our data.
%
%give the detailed example i have thought up.
%
%becons placed at distances
%
%\begin{figure*}[]
%\centering
%\includegraphics[width=2.75in]{../figures/dist_per.pdf}
%\includegraphics[width=2.75in]{../figures/sky_per.pdf}
%\caption{schematic figure of the signal to detect in 2 dimensions. ra,dec in arbitrary units. red circle in middle is the home system}
%\label{fig:2d}
%\end{figure*}
%
%
%for clarity, this is what the ideal signal might look like on the sky
%
%
%this type of beacon network is advantageous because it points directly back towards their home. only a few systems actually need to be transiting from any given line of sight.
%
%NOW THE FULL SIMULATION...
%- computation to do: if had 100 beacons, each placed at random orbital alignment, in 3d sphere around home system.
%- assume G stars, 
%- odds of observing transit of a fixed sized object versus orbital distance... goes down. need that plot to figure out probability. 
%- assume ET places beacons with uniform RADIAL density in 3d space out to some maximum distance (even \# of systems as function of radial distance) in bins of 10pc out to 100 pc (i.e. 10 beacons in each 10pc bin)
%- orbital period is exact for each system, no bins of period
%- do Monte Carlo sim with these parameters to figure out how many transiting systems we'd observe 
%
%---- make the plot for one MC realization of RA,Dec.... open circles for systems with no observed transits, colored for transits
%
%\begin{figure}[]
%\centering
%\includegraphics[width=3in]{../figures/3d_model.pdf}
%\caption{the model in 3 dimensions projected into the sky plane. 1000 simulated systems that span the galactic distance of 5-50 pc (blue) with 10 recovered transits highlighted (red). these would be hot Jupiters at the short P end.}
%\label{fig:3d}
%\end{figure}
%
%
%IDEA:
%could improve the efficiency of these beacons if we consider a bit of galactic structure, aligning the median orbital inclinations of the beacon systems with the Galactic plane, and only allowing a smaller range of possible inclinations. How much more efficient would it be if we forced $i<10^\circ$, instead of $i<90^\circ$?
%
%for a million system model w/ 90deg max, 0.46\% total detection efficiency. 
%by constraining the inclination to 10deg max, get 4.3\% detection efficiency of planets. 30deg max gets 1.4\%
%
%
%PROBLEM:
%as \citet{forgan2017} note, an interstellar communications based on transits may only be stable for $\sim$10,000 years due to evolution of planetary orbits and relative motion between stars within the Milky Way. The beacon systems centered around the host system would have to be traveling as a moving group to maintain their respective trilateration signals, or have the transiting bodies actively over time. In other words, as the beacon systems moved relative to the ET host star due to differing Galactic orbits, the semi-major axis of the transiting bodies would have to be adjusted to compensate.
%

@@

The author thanks Nicholas M. Law and Jason T. Wright for their helpful ongoing conversations in developing this idea, and Andrew P. V. Siemion and the Berkeley SETI Research Center team for hosting me for an enlightening and motivating visit.

JRAD acknowledges support from the DIRAC Institute in the Department of Astronomy at the University of Washington. The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.

>>>>

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example: Distribution of Transiting Exoplanets in the {\it Kepler} Field}
\label{sec:transit}

@@

The easiest conceptual method to search for a technosignature beacon in the spatial distribution of exoplanets would be looking for over-densities, i.e. regions with an unusually large number of transiting systems. However this requires a large and very uniform sampling of exoplanets per square degree to determine if the density is unusual. Such spatially uniform samples are difficult to achieve since e.g. bright stars can saturate large regions.

Another simple statistical test is to measure the distribution of exoplanet systems using the two-point angular correlation function \citep{landy1993}. This method measures the probability of finding two sources separated by a given radial distance, and is often used in cosmology to characterize the distribution of galaxies on cosmological scales,. The two-point correlation function is easily measured thanks to generalized functions from packages such as {\tt astroML} \citep{astroMLText}, and  more efficient approaches have been produced that can scale to very large datasets \citep[e.g.][]{wang2013}.

In Figure \ref{fig:2pt} I show the two-point correlation function for a sample of

@@

@@

J.R.A.D. thanks Nicholas M. Law and Jason T. Wright for their helpful ongoing conversations in developing this idea, and Andrew P. V. Siemion and the Berkeley SETI Research Center team for hosting me for an enlightening and motivating visit.

J.R.A.D. acknowledges support from the DIRAC Institute in the Department of Astronomy at the University of Washington. The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.

This paper includes data collected by the Kepler mission. Funding for the Kepler mission is provided by the NASA Science Mission directorate.

This research has made use of the NASA Exoplanet Archive, which is operated by the California Institute of Technology, under contract with the National Aeronautics and Space Administration under the Exoplanet Exploration Program.
